\plaintitle

### 2017-01-11 drafts/labor/complexity.tex
small wording changes on final read-through

\subsubsection{\crowdworkpers}
\topic{\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks~\cite{crowdForgeKittur}.}
Their work demonstrated proof--of--concept crowdsourcing of
an encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling,
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation workflows~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a}.

>>>>

\subsubsection{\crowdworkpers}
\topic{\citeauthor{crowdForgeKittur} were among the first to ask
whether crowdsourcing could be used for more than parallelizing tasks~\cite{crowdForgeKittur}.}
Their work showed that it could, with proof--of--concept crowdsourcing of
encyclopedia articles and news summaries
--- tasks which could be verified or repeated
with reasonable expectations of similar results.
Seeking to raise the complexity ceiling,
researchers have since created
yet more applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a}.

### 2017-01-11 drafts/labor/introduction.tex
small wording changes on final read-through

\topic{The past decade has seen a flourishing of computationally--mediated labor.}
A framing of work into modular, pre-defined components
enables computational hiring and management of workers at scale~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
In this regime, distributed workers engage in work whenever their schedules allow,
often with little to no awareness of the broader context of the work, and
often with fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.

@@

The realization that complex goals can be accomplished by directing crowds of workers has spurred industry to flock to sites of labor
such as AMT to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems that enable new forms of production
(e.g. \cite{bernsteinSoylent,vizwiz,paolacci2010running}) and pursuing social scientific inquiry into the workers on these platforms~\cite{Ross,whoareNOTtheTurkers}.
This research has identified the sociality of gig work~\cite{crowdcollab},
as well as the frustration and disenfranchisement that these systems embody~\cite{turkopticon,martin2014being,takingAHITMcInnis}.
Others have focused on the \textit{outcomes} of this frustration,
reflecting on the resistance that workers express against digitally--mediated labor markets~\cite{uberAlgorithm,dynamo}.

\topic{This body of research has broadly worked toward the answer to one central question:
\textit{What does the future hold for on--demand work and those who do it?}}
Researchers have offered insights on this question along three major threads:
First, \namerefl{sec:complexity} ---
specifically, how complex are the goals that crowd work can accomplish, and
what kinds of goals and industries may eventually utilize it~\cite{suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}?
Second, \namerefl{sec:decomposition}~\cite{sensitiveTasks,LykourentzouPersonalityMatters,Law:2016:CKC:2858036.2858144,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}?
And third, \namerefl{sec:relationships}~\cite{turkopticon,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}?

@@

\begin{table*}[t]
  \centering
  \begin{tabularx}{\textwidth}{l X X X}
    \toprule
    & \textit{Observations in piecework} & \textit{Mechanism} & \textit{Implications for On--demand Work} \\
    \midrule
    {Complexity} &
    \small{Growth from simple tasks such as sewing to more complex composite outcomes on the assembly line floor.} &
    \small{Complexity was limited by what could be easily measured and evaluated for payment by the piece.} &
    \small{Measurement and verification remain challenges and will limit complexity unless solved.} \\ \hline

@@

\subsection{Piecework as a lens to understand on--demand work}
In this paper, we offer a framing for on--demand work as a contemporary instantiation of \textit{piecework},
a work and payment structure which breaks tasks down into discrete jobs,
wherein payment is made for \textit{output}, rather than for \textit{time}.
We are not the first to relate on--demand work to piecework: in \citeyear{crowdworkFuture}, for example,
\citeauthor{crowdworkFuture} referenced crowd work as piecework briefly
as a loose analogy~\cite{crowdworkFuture}.
Our goal in this paper is to inspect the relationship much more closely.
But more than this,
the framing of on--demand labor as a reinstantiation of piecework 
gives us years of historical material to help us make sense of this new form of work, and
allows us to reflect on--demand work through a theoretical lens that is informed by years of rigorous, empirical research.

More concretely, by interrogating on--demand labor as
an instantiation or even a continuation of piecework, we can make sense of past events as part of a much larger series of an interrelated phenomena (Table~\ref{tab:overview}).
We can reflect on differences in the features that impacted piecework historically and on--demand work today.
And, to some extent, we can use these differences to offer some predictions of what on--demand work researchers
and workers themselves
might expect to see on the horizon.
For example, we will draw on the piecework literature regarding task decomposition,
which was historically limited by shortcomings in measurement and instrumentation, and
leverage that understanding to suggest how modern technology affects this mechanism in on--demand work
--- namely, by enabling precise tracking and measurement via algorithms and software.

>>>>

\topic{The past decade has seen a flourishing of computationally--mediated labor.}
A framing of work into modular, pre--defined components
enables computational hiring and management of workers at scale~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
In this regime, distributed workers engage in work whenever their schedules allow,
often with little to no awareness of the broader context of the work, and
often with fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.

@@

The realization that complex goals can be accomplished by directing crowds of workers has spurred firms to explore sites of labor
such as AMT to find the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems that enable new forms of production
(e.g. \cite{bernsteinSoylent,vizwiz,paolacci2010running}) and pursuing social scientific inquiry into the workers on these platforms~\cite{Ross,whoareNOTtheTurkers}.
This research has identified the sociality of gig work~\cite{crowdcollab},
as well as the frustration and disenfranchisement that these systems effect~\cite{turkopticon,martin2014being,takingAHITMcInnis}.
Others have focused on the responses to this frustration,
reflecting on the resistance that workers express against digitally--mediated labor markets~\cite{uberAlgorithm,dynamo}.

\topic{This body of research has broadly worked toward the answer to one central question:
\textit{What does the future hold for on--demand work and those who do it?}}
Researchers have offered insights on this question along three major threads:
First, \namerefl{sec:complexity} ---
specifically, how complex are the goals that crowd work can accomplish, and
what kinds of industries may eventually utilize it~\cite{suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}?
Second, \namerefl{sec:decomposition}~\cite{sensitiveTasks,LykourentzouPersonalityMatters,Law:2016:CKC:2858036.2858144,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}?
And third, \namerefl{sec:relationships}~\cite{turkopticon,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}?

@@

\begin{table*}[t]
  \centering
  \begin{tabularx}{\textwidth}{l X X X}
    \toprule
    & \textit{Observations in piecework} & \textit{Mechanism} & \textit{Implications for On--demand Work} \\
    \midrule
    {Complexity} &
    \small{Growth from simple tasks such as sewing to more complex composite outcomes on the assembly line floor.} &
    \small{Complexity was limited to tasks that could be easily measured and evaluated for payment by the piece.} &
    \small{Measurement and verification will remain persistent challenges that will limit complexity unless solved.} \\ \hline

@@

\subsection{Piecework as a lens to understand on--demand work}
In this paper, we offer a framing for on--demand work as a contemporary instantiation of \textit{piecework},
a work and payment structure which breaks tasks down into discrete jobs,
wherein payment is made for \textit{output}, rather than for \textit{time}.
We are not the first to relate on--demand work to piecework: in \citeyear{crowdworkFuture}, for example,
\citeauthor{crowdworkFuture} referenced crowd work as piecework briefly
as a loose analogy~\cite{crowdworkFuture}.
Our goal in this paper is to inspect the relationship much more closely.
But more than this,
the framing of on--demand labor as a reinstantiation of piecework 
gives us years of historical material to help us make sense of this new form of work, and
allows us to study on--demand work through a theoretical lens that is informed by years of rigorous, empirical research.

More concretely, by positioning on--demand labor as
an instantiation or even a continuation of piecework, we can make sense of past events as part of a much larger series of interrelated phenomena (Table~\ref{tab:overview}).
We can reflect on differences in the features that impacted piecework historically and on--demand work today.
And, to some extent, we can use these differences to offer some predictions of what on--demand work researchers
and workers themselves
might expect to see on the horizon.
For example, we will draw on piecework's scholarship on task decomposition,
which was historically limited by shortcomings in measurement and instrumentation, and
leverage that insight to suggest how modern technology affects this mechanism in on--demand work
--- namely, enabling precise tracking and measurement via algorithms and software.

### 2017-01-11 drafts/labor/trackingWork.tex
cleaned up intro a bit
small wording changes on final read-through

\documentclass[chi_draft]{sigchi}

@@

\setlist{nolistsep}
\def\plaintitle{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
% \def\plaintitle{Crowd Work and Gig Work [as] Seen Through the Historical Lens of Piecework}
\def\plainauthor{Ali Alkhatib, Michael S. Bernstein, Margaret Levi}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing; on--demand labor; gig work}
\def\plaingeneralterms{Documentation, Standardization}

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{The perspective of piecework}
\newcommand{\crowdworkpers}{The perspective of on--demand work}
\newcommand{\whatchanged}{Comparing the phenomena}
\newcommand{\implication}{Implications for on--demand work}
\newcommand{\pieceworkdefinition}{piecework is the paradigm of renumeration that is largely made compelling for its use of
``payment for results'',
leading to and leveraging narrower skill sets required for narrowly defined tasks,
and affording workers some amount of freedom to complete tasks
(and consequently earn money)
at at whatever rate and in whichever manner they wish} % do i use this more than once? even that much?

@@

\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\balance{}
\printbibliography

>>>>

\documentclass{sigchi}

@@

\setlist{nolistsep}
\def\plaintitle{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
% \def\plaintitle{Crowd Work and Gig Work [as] Seen Through the Historical Lens of Piecework}
\def\plainauthor{Ali Alkhatib, Michael S. Bernstein, Margaret Levi}
\def\emptyauthor{}
\def\plainkeywords{Crowd work; gig work; on--demand work; piecework}
\def\plaingeneralterms{Group and Organization Interfaces}

@@

\newcommand{\subsubsubsection}[1]{\textit{#1}}
\newcommand{\pieceworkpers}{The perspective of piecework}
\newcommand{\crowdworkpers}{The perspective of on--demand work}
\newcommand{\whatchanged}{Comparing the phenomena}
\newcommand{\implication}{Implications for on--demand work}
\newcommand{\pieceworkdefinition}{piecework is the paradigm of remuneration that is largely made compelling for its use of
``payment for results'',
leading to and leveraging narrower skill sets required for narrowly defined tasks,
and affording workers some amount of freedom to complete tasks
(and consequently earn money)
at at whatever rate and in whichever manner they wish} % do i use this more than once? even that much?

@@

\begin{document}
\CopyrightYear{2017} 
\setcopyright{acmlicensed}
\conferenceinfo{CHI 2017,}{May 06 - 11, 2017, Denver, CO, USA}
\isbn{978-1-4503-4655-9/17/05}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/3025453.3025974}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

% \balance{}
% \printbibliography
